Online Source Code Reuse: A Case Study of Stackoverflow \textit{vs.~}Qualitas OSS

### 2016-07-23 latex/stackoverflow.tex
Updated the venn diagram (not finished) and the 528 ok pairs (not finished of finding duplicates)

\begin{table}[h]
	\centering
	\caption{Agreed good-match(0.7) cloned pairs between Simian and Nicad}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 1 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 3 & 5 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{Agreed ok-match(0.7) cloned pairs between Simian and Nicad}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

>>>>

\begin{table}[h]
	\centering
	\caption{18 agreed good-match(0.7) cloned pairs between Simian and Nicad (14 are unique)}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 1 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 3 & 5 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}
